Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-10-06 grove-paper.tex
Finish figure renumbering

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{22}$" [> "R$_{21}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   "$\texttt{y}_{24}$" [> "R$_{23}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{22}$" [> "R$_{21}$"],
    "$\texttt{y}_{24}$" [> "R$_{23}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
TODO: show UI
\caption{User interface showing the multi-child conflict in \autoref{fig:Multi-child-d}}
\label{fig:Multi-child-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
TODO: UI (at least moc up)
\caption{Initial code}
\label{fig:Multi-parent-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{w}_{20}$" [> "R$_{25}$"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-parent-a} after Alice ... TODO}
\label{fig:Multi-parent-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'],
   "$\texttt{w}_{20}$" [> "R$_{27}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-child-a} after Bob ... TODO}
\label{fig:Multi-parent-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{$\texttt{+}_{10}$} [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    b/"$\texttt{w}_{20}$" [> "R$_{25}$"']
   },
   {}
  }
 },
};
\path [edge style,->] (a) to ["R$_{27}$",out=-60,in=60] (b);
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-parent-b} with \autoref{fig:Multi-parent-c}}
\label{fig:Multi-parent-d}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   v2/"$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{w}_{20}$" [> "R$_{25}$"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code TODO: move to previous figure}
\label{fig:Multi-parent-e}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-parent conflicts}
\label{fig:Multi-parent}
\end{figure*}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"$\texttt{+}_{10}$" [> "Root$_{9}$"'] -> {
   v2/"$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by copy as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"$\texttt{+}_{10}$" [> "Root$_{9}$"'] -> {
   v2/"$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{+}_{30}$" [> "R$_{29}$"] -> {
     "$\texttt{*}_{32}$" [> "L$_{31}$"'] -> {
      {},
      {}
     },
     {}
    }
   },
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by copy as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   v2/"$\texttt{*}_{2}$" [> "L$_{21}$"'],
   {}
  }
 }
};
\path[edge style,->] (v2) to ["R$_{29}$",out=-60,in=-60] (v8);
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by reference as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Single-User Cycles}
\label{fig:Single-User Cycles}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{19}$"'] -> {
    "$\texttt{+}_{4}$" [> "L$_{19}$"'],
    "$\texttt{*}_{6}$" [> "R$_{19}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{19}$"'] -> {
   },
   {
    "$\texttt{+}_{4}$" [> "R$_{19}$"] -> {
     "$\texttt{*}_{6}$" [> "L$_{19}$"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{19}$"'] -> {
   },
   {
    "$\texttt{*}_{6}$" [> "R$_{19}$"] -> {
     "$\texttt{+}_{4}$" [> "L$_{19}$"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{19}$"'] -> {
   },
   {
    v1/"$\texttt{*}_{6}$" [> "R$_{19}$"],
    v2/"$\texttt{+}_{4}$" [> "R$_{19}$"]
   }
  }
 }
};
\path[draw,->] (v1) to [out=-45,in=-135] (v2);
\path[draw,->] (v2) to [out=-90,in=-90] (v1);
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-User Cycles}
\label{fig:Multi-User Cycles}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{19}$"'],
   "$\texttt{*}_{6}$" [> "R$_{19}$"]
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{19}$"'] -> {
    {},
    "$\texttt{*}_{6}$" [> "R$_{19}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"] -> {
   {},
   "$\texttt{*}_{6}$" [> "R$_{19}$"] -> {
    "$\texttt{+}_{2}$" [> "L$_{19}$"'],
    {}
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{8}$" [> "Root$_{7}$"]
 }
};
\path (-1cm,-3cm) graph[graph style] {
 times/"$\texttt{*}_{6}$" [> "L$_{19}$"']
};
\path (1cm,-3cm) graph[graph style] {
 plus/"$\texttt{+}_{2}$" [> "L$_{19}$"']
};
\path[draw,->] (times) to [out=45,in=135] (plus);
\path[draw,->] (plus) to [out=-135,in=-45] (times);
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Disconnection}
\label{fig:Disconnection}
\end{figure*}

>>>>

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{24}$" [> "R$_{23}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Alice ... TODO}
\label{fig:Multi-child-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   "$\texttt{y}_{26}$" [> "R$_{25}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Editing Nested Parts of the Code-c} after Bob ... TODO}
\label{fig:Multi-child-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    "$\texttt{v}_{18}$" [> "R$_{17}$"]
   },
   {
    "$\texttt{x}_{24}$" [> "R$_{23}$"],
    "$\texttt{y}_{26}$" [> "R$_{25}$"]
   }
  }
 }
};
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-child-a} with \autoref{fig:Multi-child-b}}
\label{fig:Multi-child-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\linewidth}
\centering
TODO: show UI
\caption{User interface showing the multi-child conflict in \autoref{fig:Multi-child-d}}
\label{fig:Multi-child-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-child conflicts}
\label{fig:Multi-child}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{w}_{20}$" [> "L$_{19}$"'],
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
TODO: UI (at least moc up)
\caption{Initial code}
\label{fig:Multi-parent-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{w}_{20}$" [> "R$_{27}$"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-parent-a} after Alice ... TODO}
\label{fig:Multi-parent-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'],
   "$\texttt{w}_{20}$" [> "R$_{29}$"]
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Multi-child-a} after Bob ... TODO}
\label{fig:Multi-parent-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  a/{$\texttt{+}_{10}$} [> "Root$_{9}$"] -> {
   "$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    b/"$\texttt{w}_{20}$" [> "R$_{27}$"']
   },
   {}
  }
 },
};
\path [edge style,->] (a) to ["R$_{29}$",out=-60,in=60] (b);
\end{tikzpicture}
\caption{The result of merging \autoref{fig:Multi-parent-b} with \autoref{fig:Multi-parent-c}}
\label{fig:Multi-parent-d}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.19\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   v2/"$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{w}_{20}$" [> "R$_{27}$"']
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code TODO: move to previous figure}
\label{fig:Multi-parent-e}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-parent conflicts}
\label{fig:Multi-parent}
\end{figure*}

@@

\begin{figure}
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"$\texttt{+}_{10}$" [> "Root$_{9}$"'] -> {
   v2/"$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    {}
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by copy as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"$\texttt{+}_{10}$" [> "Root$_{9}$"'] -> {
   v2/"$\texttt{*}_{2}$" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{+}_{32}$" [> "R$_{31}$"] -> {
     "$\texttt{*}_{34}$" [> "L$_{33}$"'] -> {
      {},
      {}
     },
     {}
    }
   },
  }
 }
};
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by copy as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.32\linewidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  v8/"$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   v2/"$\texttt{*}_{2}$" [> "L$_{21}$"'],
   {}
  }
 }
};
\path[edge style,->] (v2) to ["R$_{31}$",out=-60,in=-60] (v8);
\end{tikzpicture}
\caption{\autoref{fig:Single-User Cycles-a} after Alice copy and pastes \Vertex{TODO} by reference as the right child of \Vertex{TODO}}
\label{fig:Single-User Cycles-c}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Single-User Cycles}
\label{fig:Single-User Cycles}
\end{figure}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{21}$"'] -> {
    "$\texttt{+}_{34}$" [> "L$_{33}$"'],
    "$\texttt{*}_{36}$" [> "R$_{35}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{21}$"'] -> {
   },
   {
    "$\texttt{+}_{34}$" [> "R$_{37}$"] -> {
     "$\texttt{*}_{36}$" [> "L$_{39}$"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{21}$"'] -> {
   },
   {
    "$\texttt{*}_{36}$" [> "R$_{41}$"] -> {
     "$\texttt{+}_{34}$" [> "L$_{43}$"'],
     {}
    }
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{21}$"'] -> {
   },
   {
    v1/"$\texttt{+}_{34}$" [> "R$_{37}$"],
    v2/"$\texttt{*}_{36}$" [> "R$_{41}$"]
   }
  }
 }
};
\path[edge style,->] (v1) to ["L$_{39}$",out=-45,in=-135] (v2);
\path[edge style,->] (v2) to ["L$_{43}$",out=-90,in=-90] (v1);
\end{tikzpicture}
\caption{Initial code}
\label{fig:Multi-User Cycles-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Multi-User Cycles}
\label{fig:Multi-User Cycles}
\end{figure*}

@@

\begin{figure*}
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{21}$"'],
   "$\texttt{*}_{36}$" [> "R$_{41}$"]
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-a}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   "$\texttt{+}_{2}$" [> "L$_{21}$"'] -> {
    {},
    "$\texttt{*}_{36}$" [> "R$_{45}$"]
   },
   {}
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-b}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"] -> {
   {},
   "$\texttt{*}_{36}$" [> "R$_{37}$"] -> {
    "$\texttt{+}_{2}$" [> "L$_{47}$"'],
    {}
   }
  }
 }
};
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-c}
\end{subfigure}
%%%%%%%%
\hfill
%%%%%%%%
\begin{subfigure}{0.24\textwidth}
\centering
\begin{tikzpicture}
\path (0cm,0cm) graph[graph style] {
 root[root style] -> {
  "$\texttt{+}_{10}$" [> "Root$_{9}$"]
 }
};
\path (-1cm,-3cm) graph[graph style] { plus/"$\texttt{+}_{2}$" };
\path ( 1cm,-3cm) graph[graph style] { times/"$\texttt{*}_{32}$" };
\path[edge style,->] (times) to ["L$_{43}$"anchor=south,out=-135,in=-45] (plus);
\path[edge style,->] (plus) to ["R$_{41}$"anchor=north,out=45,in=135] (times);
\end{tikzpicture}
\caption{Initial code}
\label{fig:Disconnection-d}
\end{subfigure}
%%%%%%%%
\hfill{}
\caption{Disconnection}
\label{fig:Disconnection}
\end{figure*}
